---
title: "Attributes PCA Analysis"
author: "Meghan Fletcher"
date: "12/22/2021"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(googlesheets4)

# For PCA:
library(ggfortify)
```

# Read in the data from Google Sheets
```{r, results=FALSE, message = FALSE, warning = FALSE, class.source = 'fold-hide', warning = FALSE}
aguion_barnacle <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1WfGsKOT0gFSN1yHUObDNSQflqd5avodSuf3kOZLTyLk/edit#gid=1947230832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Aguion",
             reference = "aguion1",
             .after = "question_id")



#######################################################################################################################
burden_sardine <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1TkB-P94xgRssmcbAuzwoh0BlDdvUfYHO7vWjK6r2pxs/edit#gid=1965519914", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Burden",
             reference = "burden1",
             .after = "question_id")



#######################################################################################################################
dickey_collas_eur <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1hfXTM5hwe0iLWQQmrc31-xruOV3SUixuxqRSuqC8ydA/edit#gid=1707192308", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Dickey_Collas",
             reference = "dickey_collas1",
             .after = "question_id")



#######################################################################################################################
eurich_clam <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZEIev1lcoD6Lxu3otzDCfbJJSiPJoZeyYbTvBXb_S9U/edit#gid=1453404713", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Eurich",
             reference = "eurich1",
             .after = "question_id")



#####################################################################################################################################
free_crab <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/12zMb5el0QAB-CdZdmdKjWw5Krbwx7farqlUvbN08HEg/edit#gid=390317686", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Free",
             reference = "free1",
             .after = "question_id")



#######################################################################################################################
#golden_madagascar <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1w99nN8C_Vd82j4Y23g2ZG_kuEh_Jc2HkW6lnLkhzeCU/edit#gid=1980661832", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "Golden",
#             reference = "golden1",
#             .after = "question_id")



#######################################################################################################################
friedman_fiji <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/13fgkP1xHZB6gZqXUBHuylaC3ImCDIDTFFjqQ8RAoV-s/edit#gid=476628697", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Friedman",
             reference = "friedman1",
             .after = "question_id")



#######################################################################################################################
#hollowed_bering_sea <- read_sheet(ss = #"https://docs.google.com/spreadsheets/d/1YOYZ9T7RR_8OkqQIWeZobhS-3yaEbKmuAVz16Nrrz9g/edit#gid=1980661832", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "Hollowed",
#             reference = "hollowed1",
#             .after = "question_id")



########################################################################################################################
kisara_squid <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1RX1iUmEKsOUmuPZkn4SMA6zts9TTPz-gi0D6XFrY1RQ/edit#gid=934077877", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Kisara",
             reference = "kisara1",
             .after = "question_id") 



###########################################################################################################################
kleisner_jfi <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1YM1wc6F0SgGIoBcTvSjVyLJquE6-6Chk1dPFoLiXuQY/edit#gid=1865610127", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Kleisner",
             reference = "kleisner1",
             .after = "question_id")



################################################################################################################################
lau_png <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/18po7Pgq5Od6Q8yCnFdSfj_Gaxii34e-WsYwBFA3RTvo/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Lau",
             reference = "lau1",
             .after = "question_id")



###############################################################################################################################
mason_iceland <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ZPs5ow4wpZgj5eP26jvoMRgD9q6VT9DEdkJfqj7UrRE/edit#gid=2142384281", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Mason",
             reference = "mason1",
             .after = "question_id")




##########################################################################################################################
mills_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1HEPT54TsR1aTNNzDtZI59zU0eb-eJfH61ujErxAFtiI/edit#gid=553950990", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Mills",
             reference = "mills1",
             .after = "question_id")



########################################################################################################################
pecl_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/11Z-SLlAS0f9Ug1Z8gLMnHkaN7hoZT1W0KMVLG8HtbXs/edit#gid=179679195", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Pecl",
             reference = "pecl1",
             .after = "question_id")



###########################################################################################################################
#schmidt_senegal <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1bUY6yII5y0FZfDRJ5lxpA7iD2p3o__2A1xsWivxwKB0/edit#gid=2000123802", 
#                           sheet = "UPDATED_S4_ResilienceAttributes",
#                           range = "A6:P61",
#                           col_names = TRUE,
#                           na = "",
#                           guess_max = 10000,
#                           trim_ws = TRUE,
#                           col_types = "c"
#                           ) %>%
#  as_tibble() %>%
#  clean_names() %>% 
#  add_column(case_study = "Schmidt",
#             reference = "schmidt1",
#             .after = "question_id") 



###############################################################################################################################
tokunaga_lobster <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1jgFZut693B14rdKbxprKtQcoh-mFlMzAktekjhvwf2Q/edit#gid=228934601", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Tokunaga",
             reference = "tokunaga1",
             .after = "question_id") 



############################################################################################################################
westfall_hms <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1DMx0Ux9Li1LhIe4ee5bbAYtJaw1vCezziRGyeERBthY/edit#gid=1818956842", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Westfall",
             reference = "westfall1",
             .after = "question_id")



###################################################################################################################################
zhao_moorea <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1-Muz76--fNv1qfdXZcBENP-agemTTySZAay9uAEO0HI/edit#gid=1980661832", 
                           sheet = "UPDATED_S4_ResilienceAttributes",
                           range = "A6:P61",
                           col_names = TRUE,
                           na = "",
                           guess_max = 10000,
                           trim_ws = TRUE,
                           col_types = "c"
                           ) %>%
  as_tibble() %>%
  clean_names() %>% 
  add_column(case_study = "Zhao",
             reference = "zhao1",
             .after = "question_id")
```


##################################################################################################################################

# Merge the datasets

```{r}
attributes_merged <- rbind(aguion_barnacle, burden_sardine, dickey_collas_eur, eurich_clam, free_crab, friedman_fiji, kisara_squid, kleisner_jfi, lau_png, mason_iceland, mills_lobster, pecl_lobster, tokunaga_lobster, westfall_hms, zhao_moorea)


```



# Clean the merged datasets 

```{r}
attributes_merged_clean <- attributes_merged %>% 
  rename(dimension=dimensions, 
         domain=new_domain, 
         attribute=resilience_attribute, 
         score=score_1_4,
         quality=information_quality, 
         importance=importance_of_attribute_in_study_system_high_medium_low, 
         work_as_described=does_the_mechanism_work_as_described_in_this_fishery_system) %>% 
# Simplify
  select(dimension, domain, case_study, reference, attribute, score, quality, importance, work_as_described) %>% 
# Remove spacer rows
  filter(!is.na(attribute)) %>% 
# Format scores
  filter(!is.na(score)) %>% 
# In order to get rid of "NA" values that were purposefully entered into the data, I used the `case_when` function to revert
  mutate(official_score = case_when(
    score == "1" ~ "1",
    score == "2" ~ "2",
    score == "3" ~ "3",
    score == "4" ~ "4",
    score == "NA" ~ "0"
  )) %>% 
  mutate(official_score=as.numeric(official_score)) %>%
  # Formate dimension
  mutate(dimension=recode_factor(dimension, 
                                 "Ecological"="Ecological",
                                 "Socio-economic"="Social-economic",
                                 "Governance-management"="Goverance")) %>% 
# Format data quality
  mutate(quality=ifelse(quality=="NA - Not relevant in this system", NA, quality),
         quality=recode_factor(quality,
                               "E - No data/information; no basis for expert judgement"="No data", ### CF used "E - No data/information; no basis for expert judgement", but JE's was different
                               "D - not confident that the answer provided reflects the true state of the system"="Low",
                               "C - fairly confident that the answer provided reflects the true state of the system"="Fair",
                               "B - limited data/information and expert judgement"="Good",
                               "A - adequate and reliable data/information"="Excellent")) %>% 
  # Format importance
  mutate(importance=stringr::str_to_sentence(importance),
         importance=factor(importance, levels=c("Low", "Medium", "High"))) %>% 
  # Create a new column to house numeric values for importance
  mutate(numeric_importance = case_when(
    importance == "Low" ~ "1",
    importance == "Medium" ~ "2",
    importance == "High" ~ "3")) %>% 
  mutate(numeric_importance=as.numeric(numeric_importance)) %>% 
  filter(!is.na(numeric_importance))
  
```


#####################################################################################################################################

# Prepare initial datasets for PCA Analysis

```{r}
# Make attributes row 1
attributes_clustering <- attributes_merged_clean %>% 
  select(case_study, dimension, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0) %>% 
  # Rename dimension and domain to be capital
  rename(Dimension = dimension, Domain = domain)
  


# Make case studies row 1
case_clustering <- attributes_merged_clean %>% 
  select(case_study, dimension, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)%>% 
  # Rename dimension and domain to be capital
  rename(Dimension = dimension, Domain = domain)
```


# PCA Analysis for all attributes (colored by dimension)


```{r}
# Prep data for PCA analysis
attributes_dimension_pca <- attributes_clustering %>%
  select(c(4:16)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(attributes_dimension_pca,
         data = attributes_clustering,
         colour = "Dimension",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.vjust = 1.2,
         loadings.label.hjust = 0.8,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "PCA Analysis of Case Study Attributes (by Dimension)")
```


# PCA Analysis for all attributes (colored by domain)

```{r}
# Prep data for PCA analysis
attributes_domain_pca <- attributes_clustering %>%
  select(c(4:16)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(attributes_domain_pca,
         data = attributes_clustering,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.hjust = 1,
         loadings.label.vjust = 0.5,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "PCA Analysis of Case Study Attributes (by Domain)")
```

##################################################################################################################################


# Breaking the PCA Analyses Down by Dimension

## PCA Analysis for Ecological Dimension (Comparing Case Studies)

```{r}
# prepare data for ecological dimension PCA analysis
ecological_data <- attributes_merged_clean %>% 
  filter(dimension == "Ecological") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0)%>% 
  # Rename dimension and domain to be capital
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
ecological_pca <- ecological_data %>%
  select(c(3:15)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(ecological_pca,
         data = ecological_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "darkgreen",
         loadings.label.hjust = 1,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, 
                                  linetype="solid", 
                                  colour ="black")) +
  labs(title = "Ecologcial Dimension PCA Analysis (Comparing Case Studies)")
```


## PCA Analysis for Socio-Economic Dimension (Comparing Case Studies)

```{r}
# prepare data for ecological dimension PCA analysis
socio_data <- attributes_merged_clean %>% 
  filter(dimension == "Social-economic") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0) %>% 
  # Rename dimension and domain to be capital
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
socio_pca <- socio_data %>%
  select(c(3:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(socio_pca,
         data = socio_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "navy",
         loadings.label.hjust = 1,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "Socio-Economic Dimension PCA Analysis (Comparing Case Studies)")
```


## PCA Analysis for Governance Dimension (Comparing Case Studies)

```{r}
# prepare data for governance dimension PCA analysis
goverance_data <- attributes_merged_clean %>% 
  filter(dimension == "Goverance") %>% 
  select(case_study, domain, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = case_study, values_from = official_score, values_fill = 0)%>% 
  rename(Domain = domain)
```


```{r}
# Prep data for PCA analysis
goverance_pca <- goverance_data %>%
  select(c(3:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(goverance_pca,
         data = goverance_data,
         colour = "Domain",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "purple",
         loadings.label.hjust = -0.2,
         frame = TRUE) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(title = "Governance Dimension PCA Analysis (Comparing Case Studies)")
```

#################################################################################################################################


# PCA with Attributes as the lines and cases as the points (Comparing Attributes)

```{r}
# Prep data for PCA analysis
case_pca <- case_clustering %>%
  select(c(4:41)) %>% 
  scale() %>% 
  prcomp()


# Create PCA plot
autoplot(case_pca,
         data = case_clustering,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "black",
         loadings.label.vjust = 1.2,
         loadings.label.hjust = 0.8) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "PCA Analysis using Case Studies as Points")
```

## Case Study PCA Analysis of Ecological Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
ecological_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Ecological") %>% 
  select(case_study, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
ecological_pca2 <- ecological_data2 %>%
  select(c(2:14)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(ecological_pca2,
         data = ecological_data2,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "darkgreen",
         loadings.label.vjust = -0.5) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Ecologcial Dimension PCA Analysis (Comparing Attributes)")
```


## Case Study PCA Analysis of Socio-Economic Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
socio_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Social-economic") %>% 
  select(case_study, attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
socio_pca2 <- socio_data2 %>%
  select(c(2:11)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(socio_pca2,
         data = socio_data2,
         colour = "case_study",
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "navy") +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Socio-Economic Dimension PCA Analysis (Comparing Attributes)")
```


## Case Study PCA Analysis of Socio-Economic Dimension (Comparing Attributes)

```{r}
# prepare data for ecological dimension PCA analysis
goverance_data2 <- attributes_merged_clean %>% 
  filter(dimension == "Goverance") %>% 
  select(case_study,  attribute, official_score) %>% 
  # Use `pivot_wider` function to decrease the number of rows and increase the number of columns
  # Also do values_fill = 0 to convert NA values to 0
  pivot_wider(names_from = attribute, values_from = official_score, values_fill = 0)
```

```{r}
# Prep data for PCA analysis
goverance_pca2 <- goverance_data2 %>%
  select(c(2:11)) %>% 
  scale() %>% 
  prcomp()

# Create PCA plot
autoplot(goverance_pca2,
         data = goverance_data2,
         colour = "case_study",
         label.size = 4,
         loadings = TRUE,
         loadings.label = TRUE,
         loadings.colour = "black",
         loadings.label.colour = "purple",
         loadings.label.hjust = -1) +
  theme_bw() +
  theme(legend.background = element_rect(fill="lightblue",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(colour = "Case Studies", title = "Governance Dimension PCA Analysis")
```















